\documentclass[11pt]{report}
\usepackage[scaled]{helvet}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lipsum}
\usepackage{inconsolata}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{setspace}
\renewcommand\familydefault{\sfdefault}
\pagenumbering{gobble}

\begin{document}

\title{Test Plan - Maze}
\author{James Viner}
\date{} %Remove date
\maketitle

\doublespacing

\pagebreak
\section*{Sample Files}
\subsubsection*{\texttt{\textcolor{red}{basic\_maze.txt}}}
A simple maze involving horizontal and vertical movement.
\subsubsection*{\texttt{\textcolor{red}{empty.txt}}}
An empty file.
\subsubsection*{\texttt{\textcolor{red}{invalid\_symbol.txt}}}
A maze with a dollar sign, which is an invalid symbol.
\subsubsection*{\texttt{\textcolor{red}{map00.txt}}}
A small, instructor-supplied sample maze.
\subsubsection*{\texttt{\textcolor{red}{map01.tx}}}
A small, instructor-supplied sample maze.
\subsubsection*{\texttt{\textcolor{red}{map02.txt}}}
A large, instructor-supplied sample maze.
\subsubsection*{\texttt{\textcolor{red}{map03.txt}}}
A large, instructor-supplied sample maze.
\subsubsection*{\texttt{\textcolor{red}{no\_solution.txt}}}
A maze without a valid path from start to end.
\subsubsection*{\texttt{\textcolor{red}{out\_of\_bound.txt}}}
A maze with a hole in the outer walls, allowing escape.
\pagebreak
\section*{Automated Test Cases}
Automated tests may be executed with {\texttt{\color{red}make check}}, which builds and runs a bash script that performs unit tests for this program. Additional test details can be found in {\texttt{\color{red}test/test.bash}}; the script may have to be made executable before running.
\pagebreak
\section*{Common Test Cases}
Prerequisites: {\texttt{\color{red}maze/}} directory does not already exist.
\subsection*{TC1: Installation}
\begin{enumerate}
  \item {\texttt{\color{red}git clone} {\color{blue}git@git.umbc.tc}}{\color{red}:tdqc/tdqc12/jviner/maze.git}
  \item {\texttt{\color{red}cd maze}}
\end{enumerate}
\textbf{Expected:} {\texttt{\color{red}maze/}} directory is created.
\subsection*{TC2: Correct branch}
\begin{enumerate}
  \item {\color{red}git branch}
\end{enumerate}
\textbf{Expected:} {\color{red}main} is default branch.
\subsection*{TC3: Build cleaning}
\begin{enumerate}
  \item {\texttt{\color{red}make}}
  \item {\texttt{\color{red}make clean}}
  \item {\texttt{\color{red}ls}}
\end{enumerate}
\textbf{Expected:} No .o files or executable files are left in directory.
\pagebreak
\section*{Project-Building Test Cases}
Prerequisites: In the project's directory; have run {\texttt{\color{red}make clean}}.
\subsection*{TC4: Build Explicit}
\begin{enumerate}
  \item {\texttt{\color{red}make maze}}
  \item {\texttt{\color{red}ls maze}}
\end{enumerate}
\textbf{Expected:} File is listed.
\subsection*{TC5: Build Implicit}
\begin{enumerate}
  \item {\texttt{\color{red}make}}
  \item {\texttt{\color{red}ls maze}}
\end{enumerate}
\textbf{Expected:} File is listed.
\subsection*{TC6: Build debugging}
\begin{enumerate}
  \item {\texttt{\color{red}make debug}}
  \item {\texttt{\color{red}readelf --debug-dump=decodedline maze}}
\end{enumerate}
\textbf{Expected:} Debugging info is listed.
\subsection*{TC7: Build profiling}
\begin{enumerate}
  \item {\texttt{\color{red}make profile}}
\end{enumerate}
\textbf{Expected:} Program build output contains -gp flags.
\pagebreak
\section*{File-Based Test Cases}
Prerequisites: In the project's directory; have run {\texttt{\color{red}make}}; sample files in {\texttt{\color{red}samp/}} folder.
\subsection*{TC8: Leak Prevention - Large sample file}
\begin{enumerate}
  \item {\texttt{\color{red}valgrind ./maze samp/map03.txt > /dev/null}}
\end{enumerate}
\textbf{Expected:} Program does not enter infinite loop, exits normally, and valgrind shows no leaks.
\subsection*{TC9: Leak Prevention - Empty file}
\begin{enumerate}
  \item {\texttt{\color{red}valgrind ./maze samp/empty.txt}}
\end{enumerate}
\textbf{Expected:} valgrind shows no leaks. Nothing is printed.
\subsection*{TC10: Leak Prevention - Nonexistent file}
\begin{enumerate}
  \item {\texttt{\color{red}valgrind ./maze samp/nonexistentfile.txt}}
\end{enumerate}
\textbf{Expected:} valgrind shows no leaks. Appropriate error message printed.
\end{document}
